Agents and you, a brief summary

### 2015-11-03 agents/summery.tex
added some very important comments.
added some text about kripke!

\documentclass{article}
\usepackage{amsmath}
\usepackage{txfonts}
\usepackage{booktabs}
\usepackage{color}
\usepackage{bussproofs}
\usepackage{graphicx}
\usepackage{pifont}
\usepackage{qtree}
\usepackage{tikz}
\usepackage{amssymb}
\usetikzlibrary{automata,arrows,positioning,calc}
\usepackage{listings}
\usepackage{hyperref}
\newenvironment{scprooftree}[1]%
{\gdef\scalefactor{#1}\begin{center}\proofSkipAmount \leavevmode}%
{\scalebox{\scalefactor}{\DisplayProof}\proofSkipAmount \end{center} }

@@

\section{Modal logic}

>>>>

\documentclass{article}
% I just added all the things, if you have problems build, try deleting the
% naggin packages, fat chance I don't even use it.
\usepackage{amsmath}
\usepackage{txfonts}
\usepackage{booktabs}
\usepackage{color}
\usepackage{bussproofs}
\usepackage{graphicx}
\usepackage{pifont}
\usepackage{qtree}
\usepackage{tikz}
\usepackage{amssymb}
\usetikzlibrary{automata,arrows,positioning,calc}
\usepackage{listings}
\usepackage{hyperref}
\newenvironment{scprooftree}[1]%
{\gdef\scalefactor{#1}\begin{center}\proofSkipAmount \leavevmode}%
{\scalebox{\scalefactor}{\DisplayProof}\proofSkipAmount \end{center} }

@@

\section{Modal logic}
% Before starting I just want to lay out the idea here, everytime I hear
% kripke, I imagine someone waving his arm and shouting KRIPKE in anger.
% Not that anyone will ever read these comments but its a funny idea.

This course was thought by John-Jules Meyer. The `theoretic' part focused
on the ideas behind the logics, while the `practical' focussed on writing
propper proofs. I guess I'll treat both in here.

There are 2 main sources of information I'll use, the slides by John Jules
and the modal logic paper for artificial intelligence by rosja mastop to help
me with the practical part. 
% In truth I didn't understand much of the practicals, just giving a bunch
% of examples is not a good way of teaching how to write proofs.
% This paper seems to explain it in a more structural way.

\subsection{Basic modal logic}
Express intensional (context/situation-sensitve) notations such as: 
Knowledge, Belief, Obligation, Action and Time.

\subsubsection{Modal langauge}

Imports all the things from propositional logic and is extended
with the modal operators ($\Box\phi,\Diamond\phi$) which can be read as:

\begin{tabular}{ll}
	Symbol & Definition \\ \toprule
	$\Box\phi$ & It is \emph{necesarry} that $\phi$ \\
	$\Diamond\phi$ & it is \emph{possible} that $\phi$

\end{tabular}

\noindent
Also $\neg\Box\neg\phi = \Diamond\phi$ and
$\neg\Diamond\neg\phi = \Box\phi$. So you could theoratically
drop one to create the other.
% where $\phi$ is an object I guess?

\paragraph{Semantics} Kripke %KRIPKE, *waves arm*.
model/frame $M=\langle S,\pi,R \rangle$

\begin{tabular}{ll}
	Symbol & Definition \\ \toprule
	% worlds implies mutability, states, well a state is by definition 
	% imutable. I'm pretty sure we want immutability in these kind 
	% off logics
	$S$ & Is a set of \emph{states (or worlds)} \\
	$\pi$ & Is a truth assignment function $\pi : S \times AT \to {tt, ff}$ \\
	$R$	& $R \subseteq S \times S$ is an \emph{accesibility relation}
\end{tabular}
